Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-24 paper/virtual_cytoplasm_v2.tex
shrinking xvg added, changes in plots, captions red texts removed

\begin{figure}[H]
\includegraphics[scale=0.5]{rmsf.pdf}
\caption{Root mean squared fluctuations (rmsf) for 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues for each chain of proteins. The average rmsf for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.\textbf{\color{red}{CAN YOU ADD THE PROTEIN NAME AS A LABEL INSIDE EACH PLOT? I THINK THE VARIABLE NAME SHOULD BE IN THE Y-AXIS (RMSF NM2)}}}
\label{fig:rmsf}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_mg.pdf}
\caption{Radial distribution function (rdf) showing the probability of finding a metabolite or an RNA around MG2+. The inset plot shows the rdf for short distance ($ r < 0.6 \,\, nm$) \color{red}{\textbf{HOW WAS STATISTICS DONE FOR THE RDFs? I DON'T SEE ERROR BARS}}}
\label{fig:avoiding_aggregation}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[scale=0.5]{rmsf.pdf}
\caption{Root mean squared fluctuations (rmsf) for 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues for each chain of proteins. The average rmsf for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\label{fig:rmsf}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=0.5]{rdf_mg.pdf}
\caption{Radial distribution function (rdf) showing the probability of finding a metabolite or an RNA around MG2+. The inset plot shows the rdf for short distance ($ r < 0.6 \,\, nm$)}
\label{fig:avoiding_aggregation}
\end{figure}
